---
title: "Pasilla Analysis in EdgeR"
author: "Duncan Brian"
date: '`r format(Sys.time(), "Last modified: %d %B, %Y")`'
output: pdf_document
---

```{r packageload, echo=FALSE, message=FALSE}
library(formatR)
```




Load edgeR and set working directory
```{r dataload, message=FALSE}
library(edgeR)
setwd("/home/participant/Course_Materials")
```

Load the count file
```{r }
datafile = system.file( "extdata/pasilla_gene_counts.tsv", package="pasilla" )
```
```{r style, echo=FALSE, message=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=65)}
datafile
```

Read the count table and print out
```{r readCounts}
pasillaCountTable = read.table(datafile, header=TRUE, row.names=1)

head(pasillaCountTable)
```

Construct the design and setup the conditions. Report how many samples were in the treated and untreated groups

```{r makeDesign}
pasillaDesign = data.frame(
  row.names = colnames( pasillaCountTable ),
  condition = c( "untreated", "untreated", "untreated",
                 "untreated", "treated", "treated", "treated" ),
  libType = c( "single-end", "single-end", "paired-end",
               "paired-end", "single-end", "paired-end", "paired-end" ) )

pasillaDesign

pairedSamples = pasillaDesign$libType == "paired-end"
countTable = pasillaCountTable[ , pairedSamples ]
condition = pasillaDesign$condition[ pairedSamples ]
```

Normalise 

```{r normalise}
y <- DGEList(counts=countTable,group=condition)
y <- calcNormFactors(y)
y <- estimateCommonDisp(y)
y <- estimateTagwiseDisp(y)
```


Do the differential expression test and print the table of top hits

```{r doDE}

et <- exactTest(y)
topTags(et)
```

Use the results of the previous code-chunk to comment on how many up and down regulated genes were found at a p-value cut-off of 0.05. [Embed your answers in this section of text quoting the p-value cut-off and number of genes]

Produce the smear plot, but hide the code

```{r plotSmear, echo=FALSE}
summary(de <- decideTestsDGE(et, p=0.05))
detags <- rownames(y)[as.logical(de)]
plotSmear(et, de.tags=detags)
abline(h = c(-2, 2), col = "blue")

```

