---
title: "Pasilla Analysis in EdgeR"
author: "Duncan Brian"
output: pdf_document
---

Put your code to load edgeR and locate the count file
setwd("/home/participant/Course_Materials"

```{r dataload, message=FALSE}
library(edgeR)

```

```{r results='hide'}
datafile = system.file( "extdata/pasilla_gene_counts.tsv", package="pasilla" )
datafile
```

```{r}
pasillaCountTable = read.table(datafile, header=TRUE, row.names=1)

head(pasillaCountTable)
```

Read the count table and print out

```{r readCounts}
```

Construct the design and setup the conditions. Report how many samples were in the treated and untreated groups

```{r makeDesign}

```

Normalise 

```{r normalise}

```


Do the differential expression test and print the table of top hits

```{r doDE}

```

Use the results of the previous code-chunk to comment on how many up and down regulated genes were found at a p-value cut-off of 0.05. [Embed your answers in this section of text quoting the p-value cut-off and number of genes]

Produce the smear plot, but hide the code

```{r plotSmear}

```

